Unbiased pangenome graphs

### 2022-09-13 manuscript/main.tex
order bias workflow

An unbiased pangenome graph would represent the alignment of all included genomes to all others.
Existing methods approximate this relationship by progressive alignment to a graph initially based on a reference genome \citep{Li:2020}, through a global structuring of the genome relationships in a neighbor joining phylogenetic tree \citep{Armstrong:2020}, or via creation of a \textit{de Bruijn} graph based on a fixed $k$-mer length \citep{Minkin_2016,Yu_2021}.
These methods limit computational costs by reducing the number of pairwise comparisons, but in turn their results depend on input genome order, selected reference, guide-tree topology, or $k$-mer length.

>>>>

An unbiased pangenome graph would represent the alignment of all included genomes to all others.
Existing methods approximate this relationship by progressive alignment to a graph initially based on a reference genome \citep{Li:2020}, through a global structuring of the genome relationships in a neighbor joining phylogenetic tree \citep{Armstrong:2020}, or via creation of a \textit{de Bruijn} graph based on a fixed $k$-mer length \citep{Minkin_2016,Sheikhizadeh_2016,Yu_2021}.
These methods limit computational costs by reducing the number of pairwise comparisons, but in turn their results depend on input genome order, selected reference, guide-tree topology, or $k$-mer length.
